\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Figure 13 replace top with left
Updated Figure 14 title

```{r}
#| fig-cap: "Assessing which of the 8 NLDR layouts on the PBMC3k data  (shown in Figure 1) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the top plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, b, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts c and e, that have small separations between oddly shaped clusters. Layout e is the best choice."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

@@

```{r}
#| echo: false
#| fig-cap: "Model in $2\\text{-}D$, on the tSNE layout, and three views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>)."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10

>>>>

```{r}
#| fig-cap: "Assessing which of the 8 NLDR layouts on the PBMC3k data  (shown in Figure 1) is the better representation using MSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-h). Layout f is universally poor. Layouts a, b, g, h that show large separations between clusters are universally suboptimal. Layout d with little separation performs well at tiny binwidth (where most points are in their own bin) and poorly as binwidth increases. The choice of best is between layouts c and e, that have small separations between oddly shaped clusters. Layout e is the best choice."
#| label: fig-pbmc-mse
#| fig-pos: H
#| out-height: 100%

@@

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the tSNE layout (a), and three views of the fit in projections from $9\\text{-}D$ (b, c, d), for the PBMC3k data ($a_1 = 0.099$, $b = 221 \\  (13, \ 17)$, $m = 92$, benchmark value to remove large edges is $0.1$). The three well-separated clusters with small separations observed in the \\gD{} layout of tSNE (@fig-NLDR-variety (e)) is also visible when visualizing the model overlaid on the data space in $9\\text{-}D$. Furthermore, there are some non-linear clusters. The model shows densed points within clusters in $9\\text{-}D$ space, which is an additional patterns not visible in the \\gD{} representation (@fig-NLDR-variety (e)). The full video is available at <https://youtu.be/5Y1hE4i7N2k>."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10

### 2024-08-26 paper.tex
Figure 13 replace top with left
Updated Figure 14 title

\caption{\label{fig-pbmc-mse}Assessing which of the 8 NLDR layouts on
the PBMC3k data (shown in Figure 1) is the better representation using
MSE for varying binwidth (\(a_1\)). Colour used for the lines and points
in the top plot and in the scatterplots represents NLDR layout (a-h).
Layout f is universally poor. Layouts a, b, g, h that show large
separations between clusters are universally suboptimal. Layout d with
little separation performs well at tiny binwidth (where most points are
in their own bin) and poorly as binwidth increases. The choice of best
is between layouts c and e, that have small separations between oddly
shaped clusters. Layout e is the best choice.}

@@

\caption{\label{fig-pbmc2-sc}Model in \(2\text{-}D\), on the tSNE
layout, and three views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\((s_1,  s_2) = (-0.050,  -0.058)\),
\(b = 300   (15,  20)\), \(m = 136\), benchmark value to remove large
edges is \(0.133\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}).}

>>>>

\caption{\label{fig-pbmc-mse}Assessing which of the 8 NLDR layouts on
the PBMC3k data (shown in Figure 1) is the better representation using
MSE for varying binwidth (\(a_1\)). Colour used for the lines and points
in the left plot and in the scatterplots represents NLDR layout (a-h).
Layout f is universally poor. Layouts a, b, g, h that show large
separations between clusters are universally suboptimal. Layout d with
little separation performs well at tiny binwidth (where most points are
in their own bin) and poorly as binwidth increases. The choice of best
is between layouts c and e, that have small separations between oddly
shaped clusters. Layout e is the best choice.}

@@

\caption{\label{fig-pbmc2-sc}Model in \gD{}, on the tSNE layout (a), and
three views of the fit in projections from \(9\text{-}D\) (b, c, d), for
the PBMC3k data (\(a_1 = 0.099\), \(b = 221 \  (13,  17)\), \(m = 92\),
benchmark value to remove large edges is \(0.1\)). The three
well-separated clusters with small separations observed in the \gD{}
layout of tSNE (Figure~\ref{fig-NLDR-variety} (e)) is also visible when
visualizing the model overlaid on the data space in \(9\text{-}D\).
Furthermore, there are some non-linear clusters. The model shows densed
points within clusters in \(9\text{-}D\) space, which is an additional
patterns not visible in the \gD{} representation
(Figure~\ref{fig-NLDR-variety} (e)). The full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}.}
